\documentclass{article}

\usepackage{amsmath}
\usepackage{siunitx}

\begin{document}

    All processes below are for ideal gas.
	
		\section{Isothermal process}
		
		\begin{align*}
			P\nu = RT\\
			P = RT/\nu			
		\end{align*}

		\section{Isobaric process}
		
		\begin{align*}
			P\nu = RT\\
            \nu = RT/P
		\end{align*}
	
		\section{Isentropic ideal gas}
		
		\subsection{Adiabatic + reversible = isentropic}
		
		Entropy balance equation:
		
		\begin{align*}
			s_i - s_e + \int_1^2\frac{\delta q}{T} + s_\text{gen} = 0			
		\end{align*}
	
		
	
		Adiabatic means $Q=0$ and reversible means $s_\text{gen}=0$. As a result,
		\begin{align*}
			s_i = s_e
		\end{align*}
	
		Therefore, adiabatic and reversible process is isentropic process.
		
		\subsection{Isentropic process relations}
	
		\begin{align*}
			\frac{T_1}{T_2} = \left(\frac{V_1}{V_2}\right)^{\gamma-1}
		\end{align*}
	
		\begin{align*}
			\frac{T_1}{T_2} = \left(\frac{P_1}{P_2}\right)^{(\gamma-1)/\gamma}
		\end{align*}
	
		where, $\gamma$ is the ratio of specific heats. $\gamma=1.4$ for air.
	
		\section{Constant volume heat transfer}
		
		No work generated. Heat is converted into thermal energy.
		 
		\begin{align*}		
			q = C_\nu(T_2 - T_1)
		\end{align*}
	
		where, $C_\nu$ is specific heat at constant volume. $C_\nu = \SI{0.718}{\kilo\joule\per\kg\kelvin}$.
		
		\subsection{Temperature and entropy relation}
	
		This equations tells that finite difference in temperature results in heat transfer. Differentially,
		\begin{align*}		
			\delta q = C_\nu\text{d}T
		\end{align*}
		Divide both sides by temperature $T$,
		\begin{align*}		
			\delta q/T &= C_\nu\text{d}T/T\\
			\text{d}s &= C_\nu\text{d}T/T
		\end{align*}	
		
		Integrate
		\begin{align*}		
			s_2 - s_1 = C_\nu\ln\frac{T_2}{T_1}
		\end{align*}
		
		For any $s$ and $T$, taking state 1 as reference,
		
		\begin{align*}		
			s - s_1 = C_\nu\ln\frac{T}{T_1}\\
			\exp(s - s_1) = \left(\frac{T}{T_1}\right)^{C_\nu}\\
			T^{C_\nu} = T_1^{C_\nu}\exp(s - s_1)\\
			T = T_1\exp(s - s_1)^{C_\nu}
		\end{align*}
	
	
	
	
	
\end{document}
